ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-12-08 proposal.tex
Update proposal.tex
I added the figures for two of the MATLAB examples and then created different subsections for the System Architecture, along with moving the block diagrams.

\todo[inline]{Place MATLAB figures for this example here. }

@@

\todo[inline]{Place MATLAB figures for this example here. }
\subsection{Example 3: Identify Linear Models Using the Command Line}
\label{sec:sysID-Example3}
This example in~\cite{example3} shows how to create models for MISO systems
using the command line. Before starting the model estimation process, the
equilibrium values of the inputs and outputs had to be taken out. The data from
each experiment also had to be separated into different iddata objects. The
example showed how to estimate and compare non-parametric impulse response,
transfer function, ARMA, state-space, and Box-Jenkins models with the measured
experimental data. The state-space model with the five-step response prediction
was the most accurate, with a best fit percentage of 85.83\%.

\todo[inline]{Place MATLAB figures for this example here. }

@@

\begin{figure}[htb]
    \centering 
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
  \caption{}
  \label{fig:steeringmodelarchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
  \caption{}
  \label{fig:brakeModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\textwidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
  \caption{}
  \label{fig:accelerationModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
  \caption{}
  \label{fig:shiftModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
  \caption{}
  \label{fig:speedControlModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
  \caption{}
  \label{fig:speedModelArchitecture}
\end{subfigure}
\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
\label{fig:subFunctionalBlock}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/img/mimoExGrady}
    \caption{Comparison of the state space model and merged SISO models with the validation data}
    \label{fig:exMIMO}
\end{figure}

@@

\todo[inline]{Place MATLAB figures for this example here. }
\subsection{Example 3: Identify Linear Models Using the Command Line}
\label{sec:sysID-Example3}
This example in~\cite{example3} shows how to create models for MISO systems
using the command line. Before starting the model estimation process, the
equilibrium values of the inputs and outputs had to be taken out. The data from
each experiment also had to be separated into different iddata objects. The
example showed how to estimate and compare non-parametric impulse response,
transfer function, ARMA, state-space, and Box-Jenkins models with the measured
experimental data. The state-space model with the five-step response prediction
was the most accurate, with a best fit percentage of 85.83\%.
\begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/img/commandLineIO}
    \caption{Inputs and outputs of the given system}
    \label{fig:exIO}
\end{figure}

@@

 \subsection{Steeering Subsystem}

 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
    \caption{Steering subsystem block diagram}
    \label{fig:steeringmodelarchitecture}
\end{figure}

 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
    \caption{Steering block diagram}
    \label{fig:steeringModelBlockDiagram}
\end{figure}

  \subsection{Brake Subsystem}
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Brake subsystem block diagram}
    \label{fig:brakeModelArchitecture}
\end{figure}

  \subsection{Acceleration Subsystem}
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
    \caption{Acceleration subsystem block diagram}
    \label{fig:accelerationModelArchitecture}
\end{figure}

  \subsection{Shift Subsystem}
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
    \caption{Shift subsystem block diagram}
    \label{fig:shiftModelArchitecture}
\end{figure}

  \subsection{Speed Subsystem}
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
    \caption{Speed subsystem block diagram}
    \label{fig:speedModelArchitecture}
\end{figure}

  \subsection{Speed Control Subsystem}
 \begin{figure}[h]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
    \caption{Speed Control subsystem block diagram}
    \label{fig:speedControlModelArchitecture}
\end{figure}

%\begin{figure}[htb]
%    \centering 
%\begin{subfigure}[b]{0.48\linewidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
%  \caption{}
%  \label{fig:steeringmodelarchitecture}
%\end{subfigure}
%\begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
%  \caption{}
%  \label{fig:brakeModelArchitecture}
%\end{subfigure}
%\\
%\begin{subfigure}[b]{0.48\textwidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
%  \caption{}
%  \label{fig:accelerationModelArchitecture}
%\end{subfigure}
%\begin{subfigure}[b]{0.48\linewidth}
%  \centering 
%  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
%  \caption{}
%  \label{fig:shiftModelArchitecture}
%\end{subfigure}
%\\
%\begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
%  \caption{}
%  \label{fig:speedControlModelArchitecture}
%\end{subfigure}
%\begin{subfigure}[b]{0.48\linewidth}
%  \centering
%  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
%  \caption{}
%  \label{fig:speedModelArchitecture}
%\end{subfigure}
%\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
%\label{fig:subFunctionalBlock}
%\end{figure}
